Zastosowanie regulatora PID i CNN do sterowania robotem Duckiebot

### 2023-09-13 article-en.tex
Add polish and english abstract

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
The paper presents the design and practical implementation by students of a control system
using a classical PID controller and a controller using artificial neural networks.
The control object is a Duckiebot robot and the task it is to perform is to drive the robot along a designated line (\emph{line follower}). The purpose of the proposed activities is to familiarize students with the advantages and disadvantages of the two controllers used and for them to acquire the ability to implement control systems in practice. 
The article briefly describes how the two controllers work, how to practically implement them, and describes how to practically implement the exercise. 
\end{abstract}

### 2023-09-13 article-pl.tex
Add polish and english abstract

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
W artykule przedstawiono projekt i praktyczną realizację przez studentów układu sterowania
z wykorzystaniem klasycznego regulatora PID i regulatora wykorzystującego sztuczne sieci neurnowe.
Obiektem sterowania jest robot Duckiebot a zadanie jakie ma realizować polega na jeździe robota wzdłuż wyznaczonej lini (\emph{linie follower}). Celem proponowanych aktywności jest zapoznanie studentów z zaletami  i wadami obydwu użytych regulatorów oraz nabycia przez nich umiejętności praktycznej realizacji układów sterowania. 
W artykule krótko opisano sposób działania obydwu regulatorów, sposób ich praktycznej implementacji oraz opisano w jaki sposób praktycznie należy zrealizować ćwiczenie. 
\end{abstract}
